\input{./HeadMatter.tex}
	
\part*{Assignment 2 (33\%) - Commercial Units}

\begin{tabularx}{\textwidth}{ |X|X| }
	\hline
	\textbf{Issue Date:} & 14$^{th}$ March 2023\\
	\hline 
	\textbf{Submission Date:}  & 23$^{rd}$ April 2023  \\
	\hline
\end{tabularx}

\section*{Assignment Outline}

This assignment will examine the following learning outcomes:

\begin{tabularx}{\textwidth}{ |c|X|c| }
	\hline
	\textbf{No.} & \textbf{Learning Outcome} & \textbf{Assessed} \\
	\hline 
	1  & Produce multi-view, isometric, and oblique drawings & Yes \\
	2  & Produce plan views; elevations, and sections of small to medium sized buildings. & Yes \\
	3  & Edit existing CAD drawings & No \\
	4  & Produce Revit generated material schedules and take-off lists & Yes \\
	5  & Use Revit to create presentation graphics and renderings & Yes \\
	\hline
\end{tabularx}

\vspace{1cm}

\begin{tabularx}{\textwidth}{ |l|X| }
	\hline 
	\textbf{Excellent (70+\%)} & Faithful recreation of the original drawings with no errors, and shows improvements over the original drawing set\\ 
	\hline
	\textbf{Good (56\% to 69\%)} & Recreation of the original drawing set with some minor errors or omissions in presentation and modelling \\
	\hline
	\textbf{Acceptable (40\% to 55\%)} & Recreation of the original drawing set with numerous minor errors or omissions in presentation and modelling that could be addressed with minimal additional work \\ 
	\hline
	\textbf{Poor ($<$40\%)} & Modelling incomplete, Views missing, Major Annotation Missing, general poor presentation of the design  \\
	\hline
\end{tabularx}

\vspace{1cm}



You are required to model a three unit retail building facility to the specification as detailed below and on the sample design drawings.  Your design will also become the part of the basis of Assignment 3.

\section*{Specification}


\begin{itemize}
	\item Your design should be similar to that shown in the attached drawings
	\item Fit out details to be provided for two of the units.  The third should show the structural make-up.
\end{itemize}


\subsection*{External Walls}
A 5 part Stacked wall with 215mm block inner leaf.  Wall-Ext-Stacked\_5-Parts(Commercial), L1 to L5, from the top down:
\begin{itemize}
	\item L1\_Wall-Ext\_102Bwk-50Air-65Ins-215DBlk-15Rnd\&P (Commercial Wall); variable height
	\item L2\_Wall-Ext\_100St-50Air-65Ins-215DBlk-15Rnd\&P (Banding); 1200mm high
	\item L3\_Wall-Ext\_20Rdr-100Blk-50Air-65Ins-215DBlk-25Ins (Plinth); 225mm high
	\item L4\_Wall-Ext\_100Blk-115Conc-215DBlk-15Rnd\&P (Rising Wall); 225mm high
	\item L5\_Wall-Ext\_440Dblk (440mm Foundation Blockwork); 1200 high
\end{itemize}




\subsection*{Internal Walls}
\begin{itemize}
	\item Generally: 100 \& 215mm blockwork
	\item Separating Walls: 215 blockwork
	\item Glazed Curtain Walls to front
\end{itemize}



\subsection*{Foundations}
\begin{itemize}
	\item 1350mm wide x 600  deep strip foundations to external walls
	\item 700mm wide x 450mm deep strip foundations to separating walls
	\item 750mm wide x 750mm long x 500mm deep Pad Foundations to columns
\end{itemize}


\subsection*{Floors}
\begin{itemize}
	\item Ground Floor: (Floor-GF-Comm\_150PFConc-100Ins-DPM-50Sand-200SHc);
	\begin{itemize}
		\item 150 Power floated concrete slab on
		\item 100mm Insulation on
		\item DPM on 
		\item 50mm Sand on 
		\item 200 Site Hardcore
	\end{itemize}   
	\item First Floor: (Floor-FF-Comm\_75SScr-150PCU);
	\begin{itemize}
		\item 75mm Structural Screed on 
		\item 150mm Precast Concrete Units
	\end{itemize} 
\end{itemize}


\subsection*{Ceilings}
3 No ceiling types to be included
\begin{itemize}
	\item 600 x 600mm grid
	\item 600 x 1200mm grid
	\item plastered compound ceiling
\end{itemize}



\subsection*{Lighting}
3 No different light fittings to be incorporated into the ceiling


\subsection*{Roof}
\begin{itemize}
	\item Roof to be Revit Standard, Basic Roof - Pitched Warm Industrial on Steel Roof trusses on Steel or Concrete columns built into walls
\end{itemize}


\subsection*{Site}
Flat toposurface of approx 90m wide x 80mm with Building Pads, some trees, cars and people




\newpage
\section*{Your Submission should contain the following}


\begin{tabularx}{\textwidth}{ |c|c|X| }
	\hline
	\textbf{Sheet Size} & \textbf{Sheet No.} & \textbf{Title} \\
	\hline 
	A1  & AR-0001 & Cover Sheet \\
	A1  & AR-0002 & Ground Floor Plan \\
	A1  & AR-0003 & First Floor Plan \\
	A1  & AR-0004 & North \& South Elevations \\
	A1  & AR-0005 & East \& West Elevations \\
	A1  & AR-0006 & Sections, Details and Schedules \\
	\hline
\end{tabularx}


\subsection*{AR-0001 - Cover Sheet}
\begin{itemize}
	\item Three Dimensional (Aerial View) of the model
	\item A list of the drawings in the design pack
	\item Cloud rendered external and internal views
\end{itemize}


\subsection*{AR-0002 - Ground Floor Plan}
\begin{itemize}
	\item Ground Floor Plan @ 1:100 with dimensions and Room Titles
\end{itemize}


\subsection*{AR-0003 - First Floor Plan}
\begin{itemize}
	\item First Floor Plan @ 1:100 with dimensions and Room Titles
\end{itemize}



\subsection*{AR-0004 - North \& South Elevations}
\begin{itemize}
	\item North \& South Elevation @ 1:100
\end{itemize}

\subsection*{AR-0005 - East \& West Elevations}
\begin{itemize}
	\item East \& West Elevation @ 1:100
\end{itemize}

\subsection*{AR-0006 - Sections, Details and Schedules:}
\begin{itemize}
	\item A longitudinal section facing East (Through Unit 1 Staircase) @ 1:100
	\item A Cross Section facing North (Facing Unit 1 \& 2 Staircases and Mezzanines)
	\item A detail view (Call-out) should be provided showing the Foundation / Stacked Wall / Floor Interface @ 1:20.  Make use of the Masking and Component tools and the 'repeating detail' functionality of Revit.  Annotation should include, at a minimum, the construction details outlined in the Specification provided.
	\item A Door schedule and a Window Schedule
\end{itemize}

Additional Sheets may be submitted if so desired.




\newpage
\section*{Presentation and Submission}

\begin{enumerate}
	\item All drawing sheets must have the LIT Built Environment logo and be clearly marked 'Educational Exercise - Not for Construction.  Your name and K-number is to be clearly identifiable on all sheets.
	\item Design drawings should be completed on a minimum of six A1 sheets at the scales stated above.  Additional sheets with detailed information or images may be submitted at your discretion.
	\item You are required to submit you project as a single Revit (.rvt) file through Moodle
	\item Drawings should show all necessary information to communicate design intent
	\item The Revit filename should be of the form used in PAS/BS 1192.  In this case, it will \textit{RARC02-\#\#\#-00-ZZ-M3-A-001-A1-P01}, where \#\#\# is replaced by the last 3 digits of your K-number. An example would be \textbf{'RARC02-920-00-ZZ-M3-A-001-A1-P01'}, for K-number K20001920.  Do not use spaces in the filename.
	\item Your drawings should show all necessary information to communicate design intent. 
\end{enumerate}

\end{document}