\input{HeadMatter.tex}
	
\part*{Assignment 2 – Duct Systems}

\begin{tabularx}{\textwidth}{ |X|X| }
	\hline
	\textbf{Issue Date:} & As stated on Moodle \\
	\hline 
	\textbf{Submission Date:}  & As stated on Moodle  \\
	\hline
\end{tabularx}


\section*{Continuous Assessment Marks}
This assignment will account for 25\% of the 100\% allocated for continuous assessment in this module

\section*{Assignment Outline}
You will start this assignment by creating a new Revit project based on the mechanical template.  You will then have to link to the Architectural model for reference.  You are required to model two duct systems, one supply system and one return system as depicted in the drawings that accompany this specification. In order to complete this work your will need to place appropriate air terminals with the flow rates modified as shown on the drawings. Both duct systems will need to be inspected and sized using the appropriate Revit tools. You are also required to create three (3) A1 drawing sheets using the LIT title block provided. These sheets should be populated with the views and schedules as shown.  Duct schedules and Duct fitting schedules are to be placed on the appropriate sheets. All drawings sheets and views are to be replicated in your assignment. This will involve creating multiple similar views and changing the view properties as necessary. You will also need to make use of the tagging functionality in Revit to indicate terminal flow rates and duct sizes.\\


The asset pack for this assignment contains the following items:
\begin{enumerate}
	\item LIT Title-block
	\item Revit Architectural Model
	\item Completed Drawing in pdf format
\end{enumerate}


\section*{Submission}
Upon completion, create a single zip file of your Revit project including the architectural model. Upload this single zip file to Moodle on or before the submission deadline.

\end{document}